mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-01 Draft1.Rmd
removed duplicate canonical

```{r, echo = TRUE}
library(rolog)
# Apply match.call to all components of a term
canonical <- function(term)
{
  if(is.call(term))
  {
    f <- match.fun(term[[1]])
    if(!is.primitive(f))
      term <- match.call(f, term)

    # Recurse into arguments
    term[-1] <- lapply(term[-1], canonical)
  }
  return(term)
}
# A custom function
g <- function(u)
{
  sin(u)
}
# # Mixture of (partially) named and positional arguments in unusual order
term <- quote(2L * integrate(low=-Inf, up=Inf, g)$value)
# mathml(canonical(term))
# # It is a bit of a mystery that R knows the result of this integral.
eval(term)
```

>>>>

```{r, echo = TRUE}
library(rolog)

# A custom function
g <- function(u)
{
  sin(u)
}
# # Mixture of (partially) named and positional arguments in unusual order
term <- quote(2L * integrate(low=-Inf, up=Inf, g)$value)
# mathml(canonical(term))
# # It is a bit of a mystery that R knows the result of this integral.
eval(term)
```
